Project assignment - Tahoe-LAFS with SHA-3 candidates

### 2010-10-27 paper/main.tex
Added possibly better explanation of python and cython

\section{Python bindings using Cython}
%What is it, how, why, alternatives?
% TODO: Hvorfor er nedenfornevnte i ASM eller C?
TAHOE-LAFS is written in python, but the SHA-3 candidate implementations found
in both the official NIST submissions and supercop are either in C or in
assembly. Therefore we need a way to make the implementations available in
Python. There a several ways to do this. Python itself includes a C-API,  
other options include SWIG, Cython and possible others.

\subsection{Python C-API}
The Python C-API is the official method of creating C-bindings for Python. The
procedure to do this includes writing entrypoints or wrappers for your C
functions in C. Then, through compiling you can acess your C-libraries and
functions through Python. The drawback with this approach, when faced with an
already existing C-library is that you have to actually write the
wrapper-functions or modify the C-library.

\subsection{Cython}
Cython tries to solve the problem of binding C-libraries and functions by the
use of Python instead of the use of C which the official API does. This is done
by only defining the entrypoints to the required C-functions and datatypes in a
Python/C/C++ hybrid syntax. Cython also allows creating new C/C++ functions,
available or not available to Python, in the same syntax. Cython works by
transforming the hybrid syntax into C/C++-code which utilises the official
Python C-API and compiling that. An expected tradeoff by using Cython is a
performance drop due to the extra layer of abstraction.

>>>>

\section{Python and Cython}
%What is it, how, why, alternatives?
% TODO: Finn en kilde på pythonting, om det trengs?
Python\footnote{\url{http://www.python.org}} is a high-level general-purpose
programming language. Python is also an interpreted language, which means that
python programs are compiled at runtime.  There exists multiple implementations
of Python, however the most common, CPython, is implemented in C. The fact that
Python is a high-level language usually means that there is performance penalty
in contrast with lower level languages, shuch as C. To remedy this problem it
is possible to write extensions to the language by using the official C-API.
This approach has been used by several cryptographic libraries for python such
as the official hashlib\footnote{\url{http://code.krypto.org/python/hashlib/}}
and pycryptopp\footnote{\url{http://tahoe-lafs.org/trac/pycryptopp}}.

Tahoe-\ac{LAFS} is written in python, but the SHA-3 candidate implementations found
in both the official NIST submissions and supercop are either in C or in
assembly. Therefore it is necessary to either implement the functions in python
or make extensions to python through the C-API. Where extensions should give
the best performance. % TODO: KILDE?

\subsection{Cython}
Cython\footnote{\url{http://www.cython.org}} is a language for writing Python
extensions in a language that closely resembles the Python language itself.
Basically what Cython does is to parse cython files and generate C source files
that utilises the Python C-API. Afterwards the generated source files can be
compiled as if they were written directly in C. A small performance tradeoff is
to be expected from this, due to the extra layer of abstraction.
